---
title: "Data Wrangling Exercise 2"
author: "Swati Jani Joshi"
date: "June 17, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Titanic

R markdown containing the complete code for the Titanic data set in exercise 2.

#### Load Data
```{r}
library(dplyr)
library(tidyr)
df <- read.csv("~/Documents/Data Wrangling/DW_2/titanic_original.csv")
```

#### 1. Port of Embarkation
```{r}
is.na(df$embarked) <- df$embarked == ""
df$embarked[is.na(df$embarked)] <- "S"
```

#### 2. Age

##### a.
```{r}
age_mean <- mean(df$age, na.rm = TRUE)
df$age[is.na(df$age)] <- age_mean
```

##### b. Other ways the missing values could have been populated by using the median value or the mode value instead of the mean value.

#### 3. Lifeboat
```{r}
is.na(df$boat) <- df$boat == ""
df$boat <- as.character(df$boat)
df$boat[is.na(df$boat)] <- "None"
```

#### 4. Cabin
##### It only makes sense to fill in the missing cabin numbers with NA. 
##### A missing value for cabin numbers most likely means that the person did not survive.
``` {r}
df$has_cabin_number <- ifelse(df$cabin == '', 0, 1)
```

#### Clean data file
```{r}
write.csv(df, file = "titanic_clean.csv")
```